---
title: "Homework_7_manning_phillip"
author: "Phillip Manning"
date: "3/19/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(broom)
file_path <- '/Users/phillipmanning/Downloads/train.csv'
train <- read_delim(delim = '|', file = file_path)
saveRDS(train, file = "/Users/phillipmanning/Downloads/train.rds")
glimpse(train)
```
## Exercise 1
### There are 1460 observations

## Exercise 2
```{r}
set.seed(29283)
train_set <- train %>% sample_frac(train, Id)
test_set <- train %>% filter(!(train%in% train$Id))
```
## Exercise 3 
```{r}
mod_0 <- lm(SalePrice ~ 1, data = train_set)

mean(train_set$SalePrice)
tidy(train)


glance(mod_0)
```
## Exercise 4
### We can assume that the three features will have a positive relationsihp with one another. The better the neighborhood, the better the house and the square footage. The relationship can be estimated lineraly, but a curve based on the smallest sum of squared roots is best to find the line of best fit. If the problem we are trying to solve is understand the Salerpice adn what factors contribute to it flucuating, then yes our features are useful. 

## Exercise 7 
```{r}
sim1a <- tibble(
  x = rep(1:10, each = 3),
  y = x * 1.5 + 6 + rt(length(x), df = 2)
)
simla_model<-lm(simla)