---
title: "COMPSCIX 415.2 Homework 3"
author: "Phillip Manning"
date: "2/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r load_packages, warning=FALSE, message=FALSE} 
library(tidyverse)


```
## Section 3.8.1

### 1. The original scatter plot didn't show all of the data on the chart. 
```{r}
  ggplot(data = mpg) + 
    geom_point(mapping = aes(x = cty, y = hwy), position = "jitter")
```

### 2. To control the amount of jittering, you variate the factor and/or the amount. jitter(x, factor = 1, amount = Null)

### 3. geom_count displays the current number of observations at a given point onto the graph, while geom_jitter applies to all points and adds more noise to them, revealing some points that otherwise would have been hidden. 

### 4.
```{r}
  ggplot(data = mpg) + geom_boxplot(mapping = aes(x = class, y = hwy))
```

## Section 3.9.1

### 2. labs() adds labels to the x or y coordinates, depending on which is choosen. 

### 4. City and highway mpg are positively correlated. coord_fixed ensures that one unit of x equals one unit of y; making sure that the plot is sized proportionately well. Coord_abline adds a straight line to the plot. 

## Section 4.4

### 1. The reason why the code doesn't work is because the first line of code has an i in variable, while the following line has the number 1. 

### 2. 

```{r} 
  ggplot(data = mpg) + 
    geom_point(mapping = aes(x = displ, y = hwy)) 
filter(mpg, cyl==8) 
filter(diamonds, carat > 3)