---
title: "COMPSCIX 415.2 Homework 5/Midterm"
author: "Phillip Manning"
date: "2/27/2018"
output: html_document
toc: true
toc_float: true 
toc_depth: 2
---
My Github repository for my assignments can be found at this URL [https://github.com/phillipmanning/compscix-415-2-assignments.git](https://github.com/phillipmanning/compscix-415-2-assignments.git

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(tidyverse)
library(rmarkdown)
library(dplyr)
file_path <- '/Users/phillipmanning/Downloads/rail_trail.txt'
txt_data <- read_delim(delim = '|', file = file_path)
saveRDS(txt_data, file = "/Users/phillipmanning/Downloads/rail_trail.rds")
glimpse(txt_data)
'rails' <-readRDS(file = 
"/Users/phillipmanning/Downloads/rail_trail.rds")
```

## The tidyverse packages

### 1. 

####  Plotting - ggplot2
####  Data munging/wrangling - dplyr
####  Reshaping (speading and gathering) data - tidyr
####  Importing/exporting data - readr

### 2. 

#### Plotting - (aes()), geom_smooth()
#### Data munging/wrangling -filter(), select()
#### Reshaping data - gather(), spread()
#### Importing/exporting data (note that readRDS and saveRDS are base R functions)-read_delim(), read_csv()


## R Basics

### 1. 
```{r}
"My_data.name___is.too00ooLong!" <- c( 1 , 2, 3 )
print(`My_data.name___is.too00ooLong!`)
```
### 2. 
```{r}
my_string <- c('has', 'an', 'error', 'in', 'it')
```

### 3. The values in the vector became strings. 

## Data import/export
### 1. 
```{r}
glimpse(`rails`)
```
### 2. 
```{r}
file_path <- '/Users/phillipmanning/Downloads/rail_trail.txt'
txt_data <- read_delim(delim = '|', file = file_path)
saveRDS(txt_data, file = "/Users/phillipmanning/Downloads/rail_trail.rds")
glimpse(txt_data)
'rails' <-readRDS(file = 
"/Users/phillipmanning/Downloads/rail_trail.rds")
glimpse(`rails`)
```

## Visualization

### 1. The sizes of the circles aren't to scale, so you can't compare them. The numbers aren't labelled with a percentage sign. Finally, adding the values together for one row doesn't equal to 100%. 

```{r}
ggplot(data = diamonds) + geom_boxplot(mapping = aes(x= cut, y = carat, fill = cut)) + xlab('Cut of Diamond') + ylab('Carat of Diamond') + coord_flip()
```

## Data munging and wrangling

### 1. 
```{r}
spread(table2, key = type, value = count)
```
### 2. mutate(diamonds, price_per_carat = price/carat)

### 3. I noticed that some of the lower valued carat diamonds have a higher price, which is counterintuitive. I think we can trust these numbers, but we still need to be cautious with the correlation between price and carat. 
```{r}
filter(diamonds, price > 10000 & carat < 1.5 )
```

## EDA

### 1. The data is from 2000 - 2015
```{r}
ggplot(data = txhousing, mapping = aes(x = year, y = sales)) + geom_point()
```

### 2.There are 46 cities represented. 

```{r}
select(txhousing, city)
txhousing %>% count(city)
```
### 3. 

### 4. I imagine there would be an positive relationship between the numbers of listings and the number of sales. 
```{r}
ggplot(data = txhousing, mapping = aes(x=listings, y=sales))  + geom_smooth()
```
### 5. 
```{r}
filter(txhousing, sales == NA,)
```
### 6. I wasnt able to figure out how to get all the cities listed onto the x axis, but I plotted the chart as columns regardless. It would have helped to zoom out, but I wasn't sure how to do that. 
```{r}
txhousing500 <-filter(txhousing, sales > 500)
select(txhousing500, city, month, sales)
ggplot(data = txhousing500, mapping = aes(x=city, y=sales)) + geom_col(position = )

```
